CGM and OGTT Categories

### 2025-03-13 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
GCT fix pancreatic status for one person
EnVision demographics

```{r setup}
#| include: false
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggpmisc)
library(pROC)
library(rspiro)
library(childsds)
library(arsenal)
library(gt)
library(reporttools)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF")
```

@@

>>>>

```{r setup}
#| include: false
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggpmisc)
library(pROC)
library(rspiro)
library(childsds)
library(arsenal)
library(gt)
library(reporttools)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

# Fix C088 pancreatic insufficiency
df$`Pancreatic insufficient`[df$ID == "C088"] <- "Yes"

### 2025-03-13 Christine Chan/EnVision CF/christine_CGM_OGTT_category.qmd
EnVision demographics

```{r setup}
#| include: false
library(gtsummary)
library(dplyr)
library(pracma)
library(ggplot2)
knitr::opts_knit$set(root.dir = "/home/timvigers/OneDrive/Vigers/CF")
```

@@

```{r}
#| label: tbl-1
#| tbl-cap: Participant characteristics (overall)
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, CFTR, weight
  ) %>%
  tbl_summary(by = redcap_data_access_group, missing_text = "Missing") %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, CFTR, weight, scully140
  ) %>%
  tbl_summary(by = scully140, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, CFTR, weight, scully180
  ) %>%
  tbl_summary(by = scully180, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

>>>>

```{r setup}
#| include: false
library(gtsummary)
library(dplyr)
library(pracma)
library(ggplot2)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
#| label: tbl-1
#| tbl-cap: Participant characteristics (overall)
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(redcap_data_access_group:fvc, bmi_perc) %>%
  tbl_summary(by = redcap_data_access_group, missing_text = "Missing") %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(redcap_data_access_group:fvc, bmi_perc, scully140) %>%
  tbl_summary(by = scully140, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(redcap_data_access_group:fvc, bmi_perc, scully180) %>%
  tbl_summary(by = scully180, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```
